---
output:
  html_document: default
  pdf_document: default
---

Red Wines Quality Analisis
========================================================

<!-- # First I add knitr options for the figure sizes sets the global -->
<!-- # heights and widths for the plots in my project. -->
<!-- # I load all the packages that I need in my analysis. -->

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}

knitr::opts_chunk$set(fig.width=9,fig.height=5,fig.path='Figs/',
                      fig.align='center',tidy=TRUE,
                      echo=FALSE,warning=FALSE,message=FALSE)

library(ggplot2)
library('psych')
library(GGally)
library(RColorBrewer)

```

<!-- # The next step is to read my csv dataset concerning red wines. -->

```{r echo=FALSE, Load_the_Data}
rdw <- read.csv("wineQualityReds (1).csv")
```

<!-- # I change a litlle bit the dataset to avoid the first column x. -->

```{r echo=FALSE, Dataset_change}
rdw <- subset(rdw, select=-c(X))
```

<!-- # After this I want to display the structure of the dataset. -->

```{r echo=FALSE, frame}
str(rdw)
```

<!-- # Then I want to display the names of each variable. -->

```{r echo=FALSE, Names}
names(rdw)
```

<!-- # Then I display the summary for each variable to have a view on the -->
<!-- # figures. -->

```{r echo=FALSE, Summary}
summary(rdw)
```

<!-- # I want to know how many wines (observation) are in my dataset. -->

```{r echo=FALSE, Number_of_Rows}
nrow(rdw)
```

<!-- # And I display the header to see how are the data structured. -->

```{r echo=FALSE, Header}
head(rdw)
```

This file has 1.599 observation with thirteen different variables. Each observation
represents a wine type and each variable a wine property.

# Univariate Plots Section

# Univariate Analysis

<!-- # I plot a chart, changing the default configuration. I choose a -->
<!-- # different bindwith and I also change the color from black to red and -->
<!-- # I add a border to have a clearer chart display. -->

```{r echo=FALSE,message=FALSE, warning=FALSE, Quality_Plot1}
qplot(x = quality, data = rdw, binwidth = 1,
      color = I('black'), fill = I('#E22C10')) +
  scale_x_continuous(limits = c(0, 9), breaks = seq(0, 9, 1))+
  ggtitle('Wine quality distribution')
```  

The 'Wine Quality' of the red wines is the first univariate plot that I have
chosen to work with. As it is mentioned in the title of this report I want
to focus in the quality of the wines and their connections to other variables.
In this first chart we see that the quality of wines varies in a range from
3 to 8. The most standard quality of the wines analyzed is 5, followed by a 
quality of level 6. More than 1.200 of the 1.599 wines analyzed are between
these two levels of quality. 

<!-- # I want to be more precise on my comments so that I run a code for -->
<!-- # summarizing the data of the quality variable. -->

```{r echo=FALSE, Summary_Quality}
summary(rdw$quality)
```

When we display the summary of this feature we see what I mentioned before.
The minimum quality level of the wines is three and the maximum quality level is
eight. The mean for all the wines without splitting it into groups is of 5.63.

<!-- # The next step is to have a look on the quality variable. I change the -->
<!-- # binwidth as I did before and the scale of the x-axis to habe a better -->
<!-- # view on the data. -->

```{r echo=FALSE,message=FALSE, warning=FALSE, Alcohol_Plot1}
qplot(x = alcohol, data = rdw, binwidth = 0.5,
      color = I('black'), fill = I('#E22C10'))+
  scale_x_continuous(limits = c(8, 15), breaks = seq(8, 14, 0.5)) +
ggtitle('Wine alcohol distribution')
```

The next step in my analysis is to observe the alcohol distribution, because I
suggest that maybe this is a factor that could be related with the quality.

In this case what we observe is that the range of alcohol in the 1.599 wines
analyzed is between eight and fifteen grades.

It's interesting here to take a deeper look, changing the binwidth to 0.5 and
the x-scale and breaking the sequence into 0.5 grades of alcohol. 

The graph is similar, but in this case we can see in detail the distribution
of the rate of alcohol per number of wines. We see that the alcohol rate of
these wines starts at 8.5 grades of alcohol. Achieving the highest number of
wines, more than 400 wines, in the rate 9.5 grades of alcohol. This is the peak
in number of wines per alcohol rate. The number of wines decreases regularly
from 9.5 until fourteen grades of alcohol. 

In this approach we see at first sight different patterns, when we compare the
quality of the wines and their alcohol rate.

<!-- # The next step is to take a look on the pH variable and for doing this -->
<!-- # I change the bindwith and I display the wines with a precise scaleail -->
<!-- # for having a detail visualization. -->

```{r echo=FALSE, warning=FALSE, pH_Plot2}
qplot(x = pH, data = rdw, binwidth = 0.01,
      color = I('black'), fill = I('#E22C10')) +
  scale_x_continuous(limits = c(2.5, 4.25), breaks = seq(2.5, 4.25, 0.1)) +
  ggtitle('Wine pH distribution')
```

What we see in this plot is the distribution of the pH in the red wines
observed. We see that the graph follows a normal distribution with it's peak
near 3.3 and 3.4. The main number of wines are in a range of 3.0 to 3.65.

<!-- # Now I want to visualiza the density of the wines channgig only the -->
<!-- #binwidth. -->

```{r echo=FALSE, Density_Plot2}
qplot(x = density, data = rdw, binwidth = 0.0001,
      color = I('black'), fill = I('#E22C10')) +
  ggtitle('Wine density distribution')
```

When we change the binwidth to a more precise binwidth we see that the
distribution of the density is not so clear to see. There are great variations
between groups of wines displayed.

<!-- #Now I want to display the volatile acidity variable. For this I have -->
<!-- #change the binwidth and the x-scale for adapt my plot -->

```{r echo=FALSE, warning=FALSE, Volatile_acidity_Plot}
qplot(x = volatile.acidity, data = rdw, binwidth = 0.1,
      color = I('black'), fill = I('#E22C10')) +
  scale_x_continuous(limits = c(0, 2), breaks = seq(0, 2, 0.1)) +
  ggtitle('Wine volatile acidity distribution')
```

When we display the volatile acidity variable regarding the quantity we find
out, that the distribution of the are between 0,1 and 1,6. while more than 900
wines are in a range from 0,3 to range 0.6, where the highest number of wines
are.

<!-- #I want to display now other variable: citric acid. I need to change the-->
<!-- #binwidth and the x-scale -->

```{r echo=FALSE, warning=FALSE, Citic_acid_Plot}
qplot(x = citric.acid, data = rdw, binwidth = 0.01,
      color = I('black'), fill = I('#E22C10')) +
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.05)) +
  ggtitle('Wine citric acid distribution')
```

What we see when we plot the citric acid variable is a very homogenous
distribuition, with a few very high peaks. Near 0, in 0,25 and in 0,5.

<!-- #Now I will display the sulphates feature changing the binwidth and the -->
<!-- #x-scale -->

```{r echo=FALSE, warning=FALSE, Sulphates_Plot}
qplot(x = sulphates, data = rdw, binwidth = 0.01,
      color = I('black'), fill = I('#E22C10')) +
  scale_x_continuous(limits = c(0, 2), breaks = seq(0, 2, 0.1)) +
  ggtitle('Wine sulphates distribution')
```

In the sulpahtes distribution what we observe has very high peaks in a range
from 0,5 to 0,7. The pyramid form in this distribution is very narrow and not.
consistent. Increasing fast from 0.3 to 0.5 very fast, while decreasing not so
fast from 0.7 onwards. It압 very interesting to see that there are some gaps in
the distribution on higher rates.

<!-- # Now I want to visualize the distribution of the fixed acidity -->
<!-- # variable. -->

```{r echo=FALSE, warning=FALSE, fixed_acidity_Plot}
qplot(x = fixed.acidity, data = rdw, binwidth = 0.1,
      color = I('black'), fill = I('#E22C10')) +
  scale_x_continuous(limits = c(4, 16), breaks = seq(4, 16, 0.5)) +
  ggtitle('Wine fixed acidity distribution')
```

When we display the distribution of the fixed acidity we see that the
distribution is similar as sulphates disribution. The peak is reach very fast.
The increasing starts from 4 to 7,5, while decreasing slowly until 16.

<!-- # What I want to show next is how the residual sugar feature -->
<!-- # distribution. -->

```{r echo=FALSE, warning=FALSE, residual_sugar_Plot}
qplot(x = residual.sugar, data = rdw, binwidth = 0.5,
      color = I('black'), fill = I('#E22C10')) +
  scale_x_continuous(limits = c(0, 16), breaks = seq(0, 16, 1)) +
  ggtitle('Wine residual sugar distribution')
```

If we display the residual sugar distribution of the red wine observed we see
that see a paralelism with the feature annalyzed before. The highest peak is
reached very fast, while decreasing slowlier and with some gaps between the
highest rates.

<!-- # The next step is to display the chlorides variable. I will change -->
<!-- # the setting binwidth and x-scale -->

```{r echo=FALSE, warning=FALSE, chlorides_Plot}
qplot(x = chlorides, data = rdw, binwidth = 0.01,
      color = I('black'), fill = I('#E22C10')) +
  scale_x_continuous(limits = c(0, 0.7), breaks = seq(0, 0.7,0.05)) +
  ggtitle('Wine chlorides distribution')
```

The distribution in this case is very narrow. The main quantity of wines shows
values between 0 to 0,1. The higest peak is reached near 0,75. the decreased is
very fast, while the lowest rates continued constant, but with gaps in the
highest rates.

<!-- # Now showing the free sulfur dioxide distribution changing some -->
<!-- # feature. -->

```{r echo=FALSE, warning=FALSE, free_sulfur_dioxide_Plot}
qplot(x = free.sulfur.dioxide, data = rdw, binwidth = 1,
      color = I('black'), fill = I('#E22C10')) +
  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 10)) +
  ggtitle('Wine free sulfur dioxide distribution')
```

Observing the free sulfur dioxide feature we observe the also the same pattern
analyzed before. The increasing is rapidly until reaching the peak in 6 while
decreasing slowly from 7 to approximately 75.

<!-- # The final plot of this section I want to display is total sulfur -->
<!-- # dioxide that I will display changing the settings. -->

```{r echo=FALSE, warning=FALSE, total.sulfur.dioxide_Plot}
qplot(x = total.sulfur.dioxide, data = rdw, binwidth = 10,
      color = I('black'), fill = I('#E22C10')) +
  scale_x_continuous(limits = c(0, 300), breaks = seq(0, 300, 20)) +
  ggtitle('Wine total sulfur dioxide distribution')
```

What we see in this last plot is also the same pattern as before. The highest 
peak is reached very fast in 20 while decreasin slowly with a great gap between
160 until 280.

### What is the structure of your dataset?

In this dataset we find 1.599 different wines with 12 different features
(fixed acidity, volatile acidity,citric acid, residual sugar, chlorides, free
sulfur dioxide, total sulfur dioxide, density, pH, sulphates and alcohol).

### What is/are the main feature(s) of interest in your dataset?

The main feature in this dataset is the quality of wine. My interest is to 
know which feature is the most relevant for improving the wine quality. I want
to answer the question: What should be change in the analyzed wines to get a
better quality of wines considering the given features?

My first suggestion is that alcohol must be related to the quality, because is
indeed an alcoholic product and quality should be somehow related to alcohol
(taste, smell...). 

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?

Other variables, as density and pH, follow a similar distribution as quality
and maybe therefore could be also be linked to the quality of the wines. The
rest of the features do not have such a similar distribution, but among them
they display similar patterns.

# Bivariate Plots Section

```{r echo=FALSE, Bivariate_Plots}
```

<!-- # The first step in this section is to have a look on pairs of -->
<!-- # variables. What happens when we display each feature in relation to -->
<!-- # the other features and I want to know what correlation they had. -->
<!-- # I run the code "pairs.panels" for doing this, changing the plot  -->
<!-- # dimensions to resize the plot srtucture. -->

```{r fig.width=9, fig.height=7}
pairs.panels(rdw)+
  theme(text = element_text(size=8)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1, size=7))
```

When we display the correlation between each pair of variables we discover
some interesting issues.

Concerning the correlation between quality and the other variables we find out
that alcohol is the stonger correlated variable within quality. The second
highest correlated variable with the quality feature is volatile acidity,
followed by the volume of sulphates.

It is also remarkable that the correlation of alchol and quality is only
moderate, while the volatile acidity and sulphates are weaker correlated.

<!-- # I decide to use a scatterplo to display the correlation of several  -->
<!-- # variables. In this fir plot the variable quality in the x-axis, -->
<!-- # while the alcohol variable is displayed in the y-axis. -->
<!-- # For doing this I use geom_jitter() so that we will have a view on -->
<!-- # density of the data. -->

```{r echo=FALSE, Qualityvsalcohol_Plot_1}
ggplot(aes(x = quality, y = alcohol), data =rdw) + 
  geom_jitter(alpha=0.5, width = 0.25, height = 0,
      color = I('#099009')) +
  geom_smooth(method = 'lm', color = 'red') +
  scale_x_continuous(limits = c(2, 9), breaks = seq(2, 9, 1))
```

What we see in this scatterplot is the relation between quality and alcohol.
In general we can agree that the range of alcohol in higher levels of quality is
very wide. In the less quality wines, in level 3, the range of alcohol is 
between 11 and 8 grades, but the range of alcohol of the best quality wine is
higher, between 9 and 14 grades. We can not conclude that a higher grade of
alcohol is a feature for a higher quality wine, but what we can assume that a 
lower level of alcohol tends to a worst quality wine.

<!-- # And then I run the Pearson압 correlation test for the same variables. -->

```{r echo=FALSE, Testqualityvsalcohol_Plot}
cor.test(rdw$quality, rdw$alcohol, method = 'pearson')
```

When we display the correlation coefficient test we observe that quality and
alcohol are two variable moderate related.

<!-- # Then I visualize also as a scatterplot the volatile acidity and -->
<!-- # quality features and it압 correlation also using the geom_jitter -->
<!-- #fuction. -->

```{r echo=FALSE, Qualityvsvolatile.acidity_Plot}
ggplot(aes(x = quality, y = volatile.acidity), data =rdw) + 
  geom_jitter(alpha=0.5, width = 0.25, height = 0,
      color = I('#099009')) +
  geom_smooth(method = 'lm', color = 'red') +
  scale_x_continuous(limits = c(2, 9), breaks = seq(2, 9, 1))
```

<!-- # And I run the Pearson압 correlation test also. -->

```{r echo=FALSE, Testqualityvsvolatile.acidity_Plot}
cor.test(rdw$quality, rdw$volatile.acidity, method = 'pearson')
```

Displaying the correlation test between quality and volatile acidity we
observe that the correlation is lower in this case than what we observe for the
correlation between quality and alcohol. This correlation is weaker.

<!-- #I will do the same for sulphates in relation to quality. -->

```{r echo=FALSE, Qualityvssulphates_Plot}
ggplot(aes(x = quality, y = sulphates), data =rdw) + 
  geom_jitter(alpha=0.5, width = 0.25, height = 0,
      color = I('#099009')) +
  geom_smooth(method = 'lm', color = 'red') +
  scale_x_continuous(limits = c(2, 9), breaks = seq(2, 9, 1))
```

```{r echo=FALSE, Testqualityvssulphates_Plot}
cor.test(rdw$quality, rdw$sulphates, method = 'pearson')
```

If we display the correlation test between the variables quality and sulphates
we see that the correlation is weaker than what we saw previously between the
volatile acidity and quality.

# Bivariate Analysis

Looking to bivariates plots and measures we observed what we suggested a
priori. We see that the quality of wine is moderate related to alcohol and we
observe that alcohol is the most related variable within the variables included
in this analysis in terms of quality. The other variables do not have such an
impact in the quality as alcohol. There are two variables: volatile acidity and
the quantity of sulphates that have also a little to moderate impact.

In the first plot of the bivariate analysis we get a lot of information. We
observe in this plot what we mentioned before concerning the alcohol quantity
and it's relation to the quality, but we discover other interesting patterns.
We see that density is moderate related to the alcohol variable, but density is
not so related to the quality, while density is moderate to high related to
volatile acidity,this happens also to the variable pH and citric acidity in
their relation to the volatile acidity. These three variables: density, pH and
citric acidity in their relation to volatile acidity show the strongest
relationship in this dataset.

# Multivariate Plots Section

<!-- # Now I start this multivariate seccion with a different view of the -->
<!-- # pairs with ggpairs setting quality as the colour factor. -->

```{r echo=FALSE, message=FALSE, Pairs.panels_Plot_Color}

rdw_subset <- rdw[,c('volatile.acidity', 'pH', 'density','quality', 'alcohol','citric.acid')]
ggpairs(rdw_subset,
        mapping=aes(colour = as.factor(quality)))
```

<!-- # The first plot I want to display separately is a multivariate plot -->
<!-- # with alcohol and volatile acidity in the axis while quality is the -->
<!-- # colour factor I use the Brewer Color Scale for this and I choose 1.5 -->
<!-- # for the size of the points in order to have a better distribution  -->

```{r echo=FALSE, mutivariate_alcohol_volatileacidity_quality}
p <- ggplot(rdw, aes(volatile.acidity, alcohol))
p + geom_point(aes(colour = factor(quality)), size = 1.5) +
  scale_color_brewer(type = "div", palette = "RdYlBu", name="Quality", direction=-1)+
  ggtitle('Alcohol vs. volatile acidity and colored by quality')

```

If we visualize the chart with three variables we will find some interesting
patterns.  In this first multivariate plot I have display in the x-axis the
volatile acidity variable, while alcohol is configured in the y-axis and the
quality variable is the color factor. In this plot we observe that the blue
points (medium quality) are in lower alcohol levels and yellow to red point are
displayed in more high alcohol levels. In other hand the volatile acidity
axis give us a more ambiguos information, because we find different levels of
quality at different levels of volatile acidity.

<!-- # The next step is doing the same as I did in the previous chart, but -->
<!-- # only changing the volatile acidity variable by pH. -->

```{r echo=FALSE, mutivariate_pH_alcohol_quality}
p <- ggplot(rdw, aes(pH, alcohol))
p + geom_point(aes(colour = factor(quality)), size = 1.5) +
   scale_color_brewer(type = "div", palette = "RdYlBu", name="Quality", direction=-1)+
ggtitle('Alcohol vs. pH and colored by quality')
```

If we change the volatile acidity variable by the pH variable we find a
similar path. The  wines shows better quality in high alcohol levels, while
worst quality in lower alcohol levels. Also the pH variable is following the
same path as volatile acidity with different levels of quality if we change
the pH variable.

<!-- # Then I display the next visualizaation as I did before. I only change -->
<!-- # the pH variable by the density feature. -->

```{r echo=FALSE, mutivariate_alcohol_density_quality}
p <- ggplot(rdw, aes(density, alcohol))
p + geom_point(aes(colour = factor(quality)), size = 1.5) +
   scale_color_brewer(type = "div", palette = "RdYlBu", name="Quality", direction=-1)+
  ggtitle('Alcohol vs. density and colored by quality')
```

But what happens when we change the pH variable by the density feature. What
we see in the y=axis related to alcohol is the same as the two plots before. The
higher the alcohol quantity in a wine the better the quality of the wine. But in
this plot we see a different pattern also. We see a more enlongated figure than 
in the two plots before. The tail of the figure show high level of alcohol, 
while low densisty levels and the color tends from green to blue (6-7 in
quality) including some quality level 8 wines, displayed in pink colour. 

<!-- # I repeat the same process as before changig density by citric acid. -->

```{r echo=FALSE, mutivariate_citricacid_alcohol_quality}
p <- ggplot(rdw, aes(citric.acid, alcohol))
p + geom_point(aes(colour = factor(quality)), size = 1.5) +
   scale_color_brewer(type = "div", palette = "RdYlBu", name="Quality", direction=-1)+
  ggtitle('Alcohol vs. citric acid and colored by quality')
```

If we display citric acid instead of the density variable, while mantaining the
other two feature as we did in the three plots before, we see that the worst
quality wines from level 3 to 5 are displayed at lower alcohol and citric acid
quantities, while it seems that increasing both variables the quality of wines
tends to be better.

<!-- # And in this last plot of this sectiorn I let alcohol out of the -->
<!-- # visualization, while using density and citric acid for the axis. -->

```{r echo=FALSE, mutivariate_citricacid_density_quality}
p <- ggplot(rdw, aes(citric.acid, density))
p + geom_point(aes(colour = factor(quality)), size = 1.5) +
  scale_color_brewer(type = "div", palette = "RdYlBu", name="Quality", direction=-1)+
  ggtitle('Density vs. citric acid and colored by quality')
```

When we display density and citric acid colored by quality we see that if the
density remains high while the citric acid remanis low, the quality of the wines
are poorer, but if we increase the citric acid, while mantaining the density in
low levels, we se that the quality remains high. 

But somehow if we increase the citric acid levels it seems that the quantity
of low density wines decrease. This could be because it should be difficult to
increase the citric acid of a wine while mantaining the density low.

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

In the multivariate analysis I observed that two variables (density
and citric acid) have an impact on the quality of wine as they interact with
alcohol together, while the third variable observed (pH) remains not so
important in its impact on the quality while interacting with the variable
alcohol.

### Were there any interesting or surprising interactions between features?

In this multivariate section we could observe that density and citric acid
show opposed patterns. While an increase in the level of citric acid seems to
improve the quality of a wine, an increase in the density of the wine shows to
have a negative impact on the quality of wines.

# Final Plots and Summary

### Plot One

<!-- # In this section I repeat the most interesting plot of each section. -->

```{r echo=FALSE, message=FALSE, warning=FALSE, Quality_Plot3}
qplot(x = quality, data = rdw, binwidth = 1,
      color = I('black'), fill = I('#E22C10'))+
  scale_x_continuous(limits = c(2, 9), breaks = seq(2,9, 1)) +
  ggtitle('Wine Quality Distribution') 
```  

### Description One

In this Exploratory Data Analysis I focus on quality. The distribution of the 
quantity of wines in relation to the quality follows a regular path of a normal 
distribution starting in level 3, achieving its peak in level 5 and then
decreasing to zero at quality level of 9. 

### Plot Two

```{r echo=FALSE, Plot_Two}
ggplot(aes(x = quality, y = alcohol), data =rdw) + 
  geom_jitter(alpha=0.5, width = 0.25, height = 0,
      color = I('#099009')) +
  geom_smooth(method = 'lm', color = 'red') +
  scale_x_continuous(limits = c(2, 9), breaks = seq(2, 9, 1)) +
  ggtitle('Correlation of alcohol vs. quality') +
  ylab("Alcohol (% by Volume)") +
  xlab("Quality Score")

```

### Description Two

What we observe in this graph and what we can confirm running the correlation
test is that alcohol is the most related feature of the 12 variables in this
dataset. The correlation coefficient following the Pearson methodology is 0.48.
This represent a moderate level of correlation, but indeed it has its logical
explanation, because wine is an alcoholic product. 

### Plot Three
```{r echo=FALSE, mutivariate_citricacid_density_quality2}
p <- ggplot(rdw, aes(citric.acid, density))
p + geom_point(aes(colour = factor(quality)), size = 1.5) +
  scale_color_brewer(type = "div", palette = "RdYlBu", name="Quality Score", direction=-1)+
  ggtitle('Density vs. citric acid and colored by quality') +
  ylab("Density (g / cm^3)") +
  xlab("Citric Acid (g / dm^3)")
```

### Description Three

What we see in this final plot is a different view of what we saw in the
multivariate section. As I mentioned in the previous section there where two
variables: density and citric acid, that as alcohol have an impact in the
quality of wines. 

Here we can see how density and citric acid interact with the variable quality.
What we see here is that, the higher the citric acid concentration and the lower
the density of a wine, the better the wine quality. While increasing the citric
acid seems more determinant than lowering the density of wines.

------

# Reflection

I started this observation focusing in the quality of the red wines. I wanted
to know what was the main feature related to the quality of wine. My first
thought was that alcohol should be a main feature, but not the only or the most
relevant feature.

After displaying all the variables in a univariate form looking for
interesting patterns and then looking for correlations between the variables
plotting and testing them, I found out that alcohol was the main feature, but
related to quality moderate.

We have to consider that wine is an alcoholic product and the
alcoholic feature of wine should be an important factor in its quality, but
without being a definitive feature at all. We have display other chemical
feature like volatile acidity, density, pH and others, but non of these features
could achieve the levels of correlation with the quality of wines as the
alcohol. Maybe this is why we should consider next, is to look for other
different features with stronger realtion to quality. This could be some
other objective variable like chemical ones or subtle, subjective or sensitive
features like taste, smell or eyesight.

The next step I wanted to take, was to look for multivariable combinations to 
have a deeper understanding in what was going on between all these variables. I
looked to the bivariate analysis and saw different feature that could have a
linked between them. As I mentioned before density is moderate related to the 
alcohol variable, but density is not so related to the quality, while density 
is moderate to high related to volatile acidity. Also the variable pH and
citric acidity are moderate to high related to the volatile acidity.
So that I want to take an in detail look at these three variables: density, pH 
and citric acidity in their relation to volatile acidity and their combination
to alcohol and quality. 

The problem I found here is how to display this combination of factor. I 
didn't know how to go on and which type of visualization could help me better.
Therefore I try to display the scatterplot matrice to search for a graph that
could help me to have this new insight, but I didn앖 get find a solution with
scatterplot matrices. 

To deal with this problem I decided to look for a way to compare three
variables and a found a way to distiguish the quality by colour, while
using each axis with two different variables.

This new approach let me know that not only alcohol could improve the quality
of a wine, but also increasing the citric.acid and lowering the density could 
improve the wine quality.
